---
title: |
    | \includegraphics[width=16cm]{files/booth_logo.jpg} 
    |
    | BUSN 41201 - Big Data - Final Project
    |
    |
    | \LARGE \textbf{PROJECT TITLE}
subtitle: |
    |
    |
    | 
    | **26 May 2024**
    | **Yi Cao, Shri Lekkala, Ningxin Zhang **
output:
  pdf_document: 
    toc: no
    includes:
      in_header: files/header.tex
  html_document:
    toc: no
---
\newpage
```{=latex}
\setcounter{tocdepth}{4}
\tableofcontents
```
Note: The full the code used in all the questions can be found in the appendix.


\newpage
```{r setup, include=FALSE}

##########################################
# Setup
##########################################

knitr::opts_chunk$set(
	echo = FALSE,
	fig.height = 4,
	fig.width = 6,
	warning = FALSE,
	cache = TRUE,
	digits = 3,
	width = 48
)
 
# Required Packages
library(tidyverse)
library(ggplot2)
library(dplyr)
library(corrplot)
```

```{r include=FALSE}
# Import the data
data = "abc"
```


## 1. Executive Summary

\newpage
## 2. Introduction

\newpage
## 3. Exploratory Analysis

### a)

### b)

\newpage
## 4. Our Question 1 ?
### A. Introduction
### B. Analysis
#### Model 1.
#### Model 2.
#### Model 3.
### C. Conclusion

\newpage
## 5. Our Question 2 ?
### A. Introduction
### B. Analysis
#### Model 1.
#### Model 2.
#### Model 3.
### C. Conclusion

\newpage
## 6. Our Question 3 ?
### A. Introduction
### B. Analysis
#### Model 1.
#### Model 2.
#### Model 3.
### C. Conclusion

\newpage
## 7. Conclusion

\newpage
## 8. Appendix

```{r, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
