---
title: "BUS 41201 Homework 3 Assignment"
author: |
    | Veronika Rockova
    | Veronika.Rockova@ChicagoBooth.edu
date: "4/22/2020"
fontsize: 10 pt
output: 
    pdf_document:
        fig_width: 6
        fig_height: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      #include = TRUE, 
                      fig.width = 6, fig.height = 4,
                      results='hide',
                      warning = FALSE,
                      cache = TRUE,
                      digits = 3,
                      width = 48) 
```
# Amazon Reviews

The dataset consists of 13 319 reviews for selected products on Amazon from Jan-Oct 2012.  Reviews include product information, ratings, and a plain text review. The data consists of three tables:

##Review subset.csv
is a table containing, for each review, its 
\begin{itemize}
\item ProductId: Amazon ASIN product code
\item UserId: ID of the reviewer
\item Score: numeric 1-5 (the number of stars)
\item Time: date of the review
\item Summary: review summary in words
\item Nrev: number of reviews by the user
\item Length: number of words in the review
\item Prod Category: Amazon product category 
\item Prod Group: Amazon product group
\end{itemize}
## Word freq.csv
is a simple triplet matrix of word counts from the review text including 
\begin{itemize}
\item Review ID: the row index of Review subset.csv
\item Word ID: the row index of words.csv
\item Times Word: how many times the word occurred in the review
\end{itemize}
## Words.csv
contains 1125 alphabetically ordered words that occur in the reviews. 




```{r data xtable, results='asis'}

library(knitr) # library for nice R markdown output


# READ REVIEWS

data<-read.table("Review_subset.csv",header=TRUE)
dim(data)

# 13319 reviews
# ProductID: Amazon ASIN product code
# UserID:  id of the reviewer
# Score: numeric from 1 to 5
# Time: date of the review
# Summary: text review
# nrev: number of reviews by this user
# Length: length of the review (number of words)

# READ WORDS

words<-read.table("words.csv")
words<-words[,1]
length(words)
#1125 unique words

# READ text-word pairings file

doc_word<-read.table("word_freq.csv")
names(doc_word)<-c("Review ID","Word ID","Times Word" )
# Review ID: row of the file  Review_subset
# Word ID: index of the word
# Times Word: number of times this word occurred in the text




```

## Question 1

We want to build a predictor of customer ratings from product reviews and product attributes. For these questions, you will fit a LASSO path of logistic regression using a binary outcome: 
\begin{align}
Y=1& \quad\text{for  5 stars}\\
Y=0& \quad \text{for less than 5 stars}.
\end{align}


Fit a LASSO model with only product categories. The start code prepares a sparse design matrix of 142 product categories. What is the in-sample R2 for the AICc slice of the LASSO path? Why did we use standardize FALSE? (1 point)



```{r data, results='asis'}


# Let's define the binary outcome

# Y=1 if the rating was 5 stars

# Y=0 otherwise

Y<-as.numeric(data$Score==5)

# (a) Use only product category as a predictor

library(gamlr)

source("naref.R") 

# Cast the product category as a factor
data$Prod_Category<-as.factor(data$Prod_Category)

class(data$Prod_Category)


# Since product category is a factor, we want to relevel it for the LASSO. 
# We want each coefficient to be an intercept for each factor level rather than a contrast. 
# Check the extra slides at the end of the lecture.
# look inside naref.R. This function relevels the factors for us.

data$Prod_Category<-naref(data$Prod_Category)

# Create a design matrix using only products

products<-data.frame(data$Prod_Category)

x_cat<-sparse.model.matrix(~., data=products)[,-1]

# Sparse matrix, storing 0's as .'s 
# Remember that we removed intercept so that each category 
# is standalone, not a contrast relative to the baseline category

colnames(x_cat)<-levels(data$Prod_Category)[-1]

# let's call the columns of the sparse design matrix as the product categories

# Let's fit the LASSO with just the product categories

lasso1<- gamlr(x_cat, 	y=Y, standardize=FALSE,family="binomial",
lambda.min.ratio=1e-3)




```


## Question 2

Fit a LASSO model with both product categories and the review content (i.e. the frequency of occurrence of words). Use AICc to select lambda.
How many words were selected as predictive of a  5 star review? Which 10 words have the most positive effect on odds of a 5 star review? What is the interpretation of the coefficient for the word `discount'? (3 points)

```{r xtable, results='asis'}

# Fit a LASSO with all 142 product categories and 1125 words 

spm<-sparseMatrix(i=doc_word[,1],
                  j=doc_word[,2],
                  x=doc_word[,3],
                  dimnames=list(id=1:nrow(data),
                  words=words))

dim(spm) # 13319 reviews using 1125 words

x_cat2<-cbind(x_cat,spm)

lasso2 <- gamlr(x_cat2, y=Y,lambda.min.ratio=1e-3,family="binomial")


```


## Question 3

Continue with the model from Question 2.
Run cross-validation to obtain the best lambda value that minimizes OOS deviance. How many coefficients are nonzero then? How many are nonzero under the 1se rule?  (1 point)

```{r xtable data, results='asis'}


cv.fit <- cv.gamlr(x_cat2,
				   y=Y,
				   lambda.min.ratio=1e-3,
				   family="binomial",
				   verb=TRUE)

 


```


