---
output:
  pdf_document: default
  html_document: default
---

# BUS 41201 Homework 5 Assignment

## Group 24: Shihan Ban, Yi Cao, Shri Lekkala, Ningxin Zhang

## 30 April 2024

### Setup

We’ll explore casts for ‘drama’ movies from 1980-1999.  
See actors example code and data.  
I’ve limited the data to actors in more than ten productions over this time period (and to movies with more than ten actors).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      #include = TRUE, 
                      fig.width = 6, fig.height = 4,
                      warning = FALSE,
                      cache = TRUE,
                      digits = 3,
                      width = 48) 
# set.seed(123)
```

```{r}
## actors network example

library(igraph)

### GRAPH
## read in a graph in the `graphml' format: xml for graphs.
## it warns about pre-specified ids, but we want this here
## (these ids match up with the castlists in movies.txt)

actnet <- read.graph("actors.graphml",format="graphml")

### TRANSACTION
## read in the table of actor ids for movies
## this is a bit complex, because the movie names
## contain all sorts of special characters.

movies <- read.table("movies.txt", sep="\t", 
	row.names=1, as.is=TRUE, comment.char="", quote="")

## it's a 1 column matrix.  treat it like a vector

movies <- drop(as.matrix(movies))

## each element is a comma-separated set of actor ids.  
## use `strsplit' to break these out

movies <- strsplit(movies,",")

## and finally, match ids to names from actnet

casts <- lapply(movies, 
	function(m) V(actnet)$name[match(m,V(actnet)$id)])

## check it

casts['True Romance']

## format as arules transaction baskets

library(arules)

casttrans <- as(casts, "transactions")


## Set up STM information

castsize <- unlist(lapply(casts, function(m) length(m)))

## see ?rep.int: we're just repeating movie names for each cast member

acti <- factor(rep.int(names(casts),times=castsize))

## actors

actj <- factor(unlist(casts), levels=V(actnet)$name)

## format as STM (if you specify without `x', its binary 0/1)

actmat <- sparseMatrix(i=as.numeric(acti),j=as.numeric(actj),
		dimnames=list(movie=levels(acti),actor=levels(actj)))

## count the number of appearences by actor

nroles <- colSums(actmat)

names(nroles) <- colnames(actmat)
```

\newpage

## Question 1

### The actors network has an edge if the two actors were in the same movie. Plot the entire actors network.

```{r}
```

## Question 2

### Plot the neighborhoods for “Bacon, Kevin” at orders 1-3.

```{r}
```

### How does the size of the network change with order?

## Question 3

### Who were the most common actors? 

```{r}
```

### Who were the most common actors? 

### Who were most connected?

### Pick a pair of actors and describe the shortest path between them.


## Question 4

### Find pairwise actor-cast association rules with at least 0.01% support and 10% confidence. Describe what you find.

```{r}
```

## [Bonus]

### What would be a regression based alternative to ARules? Execute it for a single RHS actor.

```{r}
```
